Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-06-27 paper/document.tex
Add author merging screenshot.

\begin{figure}[!h]
\centering
\includegraphics[width=\columnwidth]{context}
\caption{Data extraction pipeline for TypeV. First, we list the commits in branch chronological order. Then we calculate the AST difference between each changed file across each pair of consecutive commits. Finally, we may visualize the information in a variety of ways.}
\label{fig:context}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[height=2.5in]{commits_view}
\caption{Commits increase in time from bottom up. Therefore, ASTs from B and C are diff'd against ASTs in A. ASTs from E are diff'd against D. Since D is a merge commit, its changes are ignored as they are recorded in C and B.}
\label{fig:commits}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{data-extracted}
\caption{Hierarchy of data extracted by TypeV. Each repository may have zero or more commits; each commit may have zero or more changed files; each changed files may have zero or more changes, as computed by our AST differencing tool.}
\label{fig:data-extracted}
\end{figure}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=\textwidth]{Screenshot_antlr4}
\caption{Screenshot showing the main view for TypeV. The data being displayed is from the ANTLR4 repository. Light blue bars \additionsbox{10pt} indicate \textbf{additions}; dark red bars \deletionsbox{10pt} indicate \textbf{deletions}.}
\label{fig:main-view}
\end{figure*}

@@

One issue with analyzing source code repositories is that authors can commit from a variety of different computers which can have different emails and usernames attached to their Git configuration. This may result in one author appearing as several different authors in the \texttt{git log}. There is no perfect way to deal with this problem; however, we added an interface for managing authors. A user can manually specify an author's various aliases using a simple dropdown list. All statistics attributed to an author's various aliases are then remapped as belonging to one canonical author as specified by the user. The author managing view also provides a facility for selecting and deselecting authors shown in the timeline. Thus, visualization users can focus on the changes made by a particular author or a group of authors, rather than having to view the changes made by all authors.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{context}
\caption{Data extraction pipeline for TypeV. First, we list the commits in branch chronological order. Then we calculate the AST difference between each changed file across each pair of consecutive commits. Finally, we may visualize the information in a variety of ways.}
\label{fig:context}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[height=2.5in]{commits_view}
\caption{Commits increase in time from bottom up. Therefore, ASTs from B and C are diff'd against ASTs in A. ASTs from E are diff'd against D. Since D is a merge commit, its changes are ignored as they are recorded in C and B.}
\label{fig:commits}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\columnwidth]{data-extracted}
\caption{Hierarchy of data extracted by TypeV. Each repository may have zero or more commits; each commit may have zero or more changed files; each changed files may have zero or more changes, as computed by our AST differencing tool.}
\label{fig:data-extracted}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=\textwidth]{Screenshot_antlr4}
\caption{Screenshot showing the main view for TypeV. The data being displayed is from the ANTLR4 repository. Light blue bars \additionsbox{10pt} indicate \textbf{additions}; dark red bars \deletionsbox{10pt} indicate \textbf{deletions}.}
\label{fig:main-view}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\columnwidth]{author-merging}
\caption{Screenshot showing the author management view for Apache Bookkeeper. Users can use a drop-down list to select the aliases for an author, and select whether to show or hide the author in the timeline view. Authors in the drop-down list are sorted in decreasing order of Jaccard similarity.}
\label{fig:author-merging}
\end{figure}

One issue with analyzing source code repositories is that authors can commit from a variety of different computers which can have different emails and usernames attached to their Git configuration. This may result in one author appearing as several different authors in the \texttt{git log}. There is no perfect way to deal with this problem; however, we added an interface for managing authors (Figure~\ref{fig:author-merging}. A user can manually specify an author's various aliases using a simple dropdown list. All statistics attributed to an author's various aliases are then remapped as belonging to one canonical author as specified by the user. The author managing view also provides a facility for selecting and deselecting authors shown in the timeline. Thus, visualization users can focus on the changes made by a particular author or a group of authors, rather than having to view the changes made by all authors.
